### 2022-03-29 Writing/Palaeontology/Reviews/response_to_reviewers.tex

\textit{we measured both the Robinson-Foulds distance (the differences in clade compositions; Robinson \& Foulds 1981) and the triplets distance (the differences in tips positions; Dobson 1975) between the trees inferred}. Lines @@@

\end{itemize}

\section{Referee 3}

\textcolor{blue}{Sadly however, I am skeptical that this paper really addresses the central issue with character correlation and inferring phylogenies.}

We are also sad that we did not address the central issue(s) with character correlation although that was never our intention. We have now specified more clearly that what this paper ``offers is an idea of what happens when there is some amount of correlated change, but we just do not know how much.'' (as correctly worded by referee 2). We believe that the issue(s!) with character correlation and inferring phylogenies have to be addressed in an incremental way and hope that this manuscript will be a step forward in that direction. We have now clarified that throughout the manuscript:

% @@@TODO-7.

\textcolor{blue}{Particularly, their main conclusion is that character correlation is a 'good' thing, i.e. having increased character correlation actually results in more accurate topologies.}

We do not claim this in the manuscript but rather that character correlation can, for specific datasets and methods, more or less bias topological inference. We have now clarified this

% @@@TODO-8.

@@

\textcolor{blue}{One of the central conclusions (from the abstract) is 'This means that datasets with low correlation between characters will make it more complicated to estimate a correct topology'. This is not a novel conclusion, nor does it really have anything to do with the issue that the authors claim to address. All this is really confirming is that inferring phylogenies from matrices that contain limited phylogenetic signal is difficult; it is not related to how correlated characters that show homoplasy impact our ability to infer accurate phylogenetic hypotheses. If character correlation really were a positive influence on topological accuracy then character matrices should be coded using a/p coding (rather than using hierarchical characters with some taxa being inapplicable for certain characters) as this coding method would maximize character correlation (e.g. Pleijel 1995, Cladistics).}

We do agree that these are valid limitations from this study and have acknowledged them more clearly:
Third, by not focusing on modeling the sources of character correlation specifically (see section “Distinction between different character correlations” above), we do not allow to distinguish the specific effect of each correlation for downstream analyses (see Sansom et al. 2017 for such an application on dental morphological data). However, these sources are often not available to authors, either because of the data availability or the resources available to the workers (i.e. time and money) and thus we here propose an approach showing the effect of character correlation when the sources of correlation are effectively unknown. Lines @@@
% @@@TODO-9

@@

\textcolor{blue}{Character correlation should only be a problem for inferring an accurate topology if the correlated characters contain misleading phylogenetic signal and change multiple times in concert on the tree, i.e. show coordinated homoplasy.  This is effectively the 'Intra-organismal dependence' type of character correlation that the authors identify in the introduction, the type of character correlation that is probably of most concern regarding inferring phylogenetic trees. This type of dependent character state change is not only an issue for morphological phylogenetics, but is likely also a problem for molecular data. For example the presence of particular amino acids at particular sites in proteins is fundamental for determining 3D protein structure, limiting the substitutions that can occur at particular sites if proteins are to maintain this 3D structure, which is similar to the tooth occlusion example that is cited in the text. This a particularly relevant and interesting example, especially given that an empirical analysis investigating the performance of dental data from mammals found that they recover phylogenies that are more in conflict with those inferred from molecular data (Sansom et al. 2017) citing character non-independence as a possible factor driving this incongruence. This paper is absent from the bibliography and should certainly be discussed, especially as the conclusions of this paper differ so radically.}

We thank the reviewer for drawing our attention to this paper (Sansom et al. 2017) and the DNA example and have now added that to our manuscript:

\textit{It is also worth noting that the evolutionary and intra-organismal dependences induced correlations are by no means restricted to the use of discrete morphological data. In fact, by essence, these correlations appear to any type of data whether continuous (e.g. linear measurements or morphometric geometric measurements) or non-morphological (e.g. behaviour, or - much more commonly used - molecular data).} Lines @@@
% @@@TODO-10: add ref to Sansom somewhere in the discussion.

@@

\textcolor{blue}{In the discussion (P6. Line 339) the authors state '(1) evolutionary correlation is implied by simulating the characters using Birth-Death trees; and (2) intra-organismal correlation is present in the matrices for the characters randomly simulated but sharing similar evolutionary simulation regimes.  However, the effect of these sources of correlation was out of the scope of this study and would have required a posteriori changes to the matrices'. This means that characters that are correlated due to shared evolutionary history and characters that show coordinated homoplasy are not distinguished by downstream analyses, limiting the applicability of the results for understanding issues raised by real world examples (such as the dental data analysis by Sansom et al. 2017, Sys Bio).}

We do agree that these are valid limitations from this study and have acknowledged them more clearly:

\textit{Third, by not focusing on modeling the sources of character correlation specifically (see section “Distinction between different character correlations” above), we do not allow to distinguish the specific effect of each correlation for downstream analyses (see Sansom et al. 2017 for such an application on dental morphological data). However, these sources are often not available to authors, either because of the data availability or the resources available to the workers (i.e. time and money) and thus we here propose an approach showing the effect of character correlation when the sources of correlation are effectively unknown.} Lines @@@

@@

\textcolor{blue}{In the conclusions the authors state: 'However, in empirical datasets, if character difference is not driven by selection (e.g. pleiotropy) correlation is likely be cancelled out if the correlated characters are randomly distributed with respect to traits.' I am not entirely sure what the authors mean by this sentence. I think that what they are suggesting is that character correlations that arise due to selection will have different impacts on accuracy of phylogenetic reconstructions vs those that arise from drift, which really is what this paper should be trying to address. Instead the analyses pool these types of character correlation rather than trying to disentangle them.}

% @@@TODO-11: specify this in the conclusion

\subsection{Simulation protocol and methodology}

\textcolor{blue}{I am not sure that I understand the logic of only comparing the results of the phylogenetic analyses to what the authors call the 'normal' tree and not the tree that generated the data. Surely the whole point of this exercise is to understand if character correlation actually results in misleading phylogenetic inferences.}

The purpose of the “normal tree” (now described as the ``topology inferred from the unperturbed matrix'') is to isolate the variables being studied. Indeed, if the whole point of the exercise is to understand if character correlation actually results in misleading signal, one must isolate that variable from all others. This difference is crucial because our methods did not directly simulate covariation. We simulated datasets and then perturbed them. Thus the experimental ‘true tree’ (now described as "the starting tree") is the one recovered by the analyses in the absence of any of our experimental perturbations. Comparison with the simulation (i.e. “starting tree”) would introduce additional stochastic variables that arose during the unperturbed simulation of the datasets. Comparisons with that tree would be unable to isolate the effects of our experimental perturbations.

\textcolor{blue}{It strikes me that the way in which they treat their morphological matrices just results in the 'minimised' matrix having the phylogenetic signal that supports the 'normal' tree reinforced as the correlated characters will essentially just contain the same phylogenetic signal that supported the 'normal' tree, though not necessarily the true tree.  For many of the simulated matrices, the normal tree could share very few clades with the tree that was used to generate the data itself, which is clearly demonstrated in O'Reilly et al 2016 (where the same binary HKY simulation method was also used). In this paper, the accuracy of the trees from downstream phylogenetic analyses are often very different to the generating tree. In any revision, I would want to see the impact of comparing the simulated matrices to the generating tree.}

We’ve added the comparisons between the trees from the modified matrices and the "starting tree" in the supplementary materials. %TG: is that done?
However, as stated above, what these results actually show is the effect of A: changing the character correlation + B: the effect of phylogenetic inference + C: the effect of simulating discrete morphological characters. This last component C is not the focus of our study (as specified on lines @@@) and thus is removed from the main manuscript. In fact, there is a really rich amount of papers trying to understand the effect of B and C with no consensus so far (i.e. simulating realistic evolutionary data is complicated AND inferring a realistic evolutionary history from real data is complicated). Therefore, we chose to only focus on A and B and correct for C by effectively comparing to the topology inferred from the unperturbed matrix rather than the starting tree (i.e. making the results relative to the ``best'' inference possible with the simulated data).

@@

\subsection{Minor/stylistic comments}

\textcolor{blue}{The merged PDF for review has identical font size for figure/table captions and the main text, making it difficult to read fluently.}

% @@@TODO-13 we have changed the font size for the figures/tables captions and the main text.

@@

\textcolor{blue}{The text has many typos, mostly pluralization (e.g. character vs characters). Randomised is misspelled in Fig 1. Please check the text and figures thoroughly.}

We have fixed the typo in figure 1 and checked the rest of the manuscript more thoroughly.
%TG: TODO

### 2022-05-16 Analysis/03-EffectCorrelationFigure.Rmd
sync

>>>>

## Branch length distribution

How are the branch lengths distributed in the initial trees?

```{r, fig.width=8, fig.height=8}
## Branch lengths for the trees with 25 taxa
plot.brlen.distribution("../Data/Simulations/Trees/", ntaxa = 25, cols = "grey", main = "Branch length distributions for \"true\" trees with 25 taxa", zeros = c(1e-16, 1e-10, 1e-05, 1e-01))
```

```{r, fig.width=8, fig.height=8}
## Branch lengths for the trees with 25 taxa
plot.brlen.distribution("../Data/Simulations/Trees/", ntaxa = 75, cols = "grey", main = "Branch length distributions for \"true\" trees with 75 taxa", zeros = c(1e-16, 1e-10, 1e-05, 1e-01))
```

```{r, fig.width=8, fig.height=8}
## Branch lengths for the trees with 25 taxa
plot.brlen.distribution("../Data/Simulations/Trees/", ntaxa = 150, cols = "grey", main = "Branch length distributions for \"true\" trees with 150 taxa", zeros = c(1e-16, 1e-10, 1e-05, 1e-01))
```

<!-- Figures for SOM: -->

```{r, fig.width=8, fig.height=8, eval = TRUE, echo = FALSE}
pdf("../Writing/Figures/Zero_brlen_25t.pdf", width = 8, height = 8)
## Branch lengths for the trees with 25 taxa
plot.brlen.distribution("../Data/Simulations/Trees/", ntaxa = 25, cols = "grey", main = "Branch length distributions for \"true\" trees with 25 taxa", zeros = c(1e-16, 1e-10, 1e-05, 1e-01))
```

```{r, fig.width=8, fig.height=8, eval = TRUE, echo = FALSE}
pdf("../Writing/Figures/Zero_brlen_75t.pdf", width = 8, height = 8)
## Branch lengths for the trees with 75 taxa
plot.brlen.distribution("../Data/Simulations/Trees/", ntaxa = 75, cols = "grey", main = "Branch length distributions for \"true\" trees with 75 taxa", zeros = c(1e-16, 1e-10, 1e-05, 1e-01))
```

```{r, fig.width=8, fig.height=8, eval = TRUE, echo = FALSE}
pdf("../Writing/Figures/Zero_brlen_150t.pdf", width = 8, height = 8)
## Branch lengths for the trees with 150 taxa
plot.brlen.distribution("../Data/Simulations/Trees/", ntaxa = 150, cols = "grey", main = "Branch length distributions for \"true\" trees with 150 taxa", zeros = c(1e-16, 1e-10, 1e-05, 1e-01))
```

### 2022-05-16 Analysis/04-EffectCorrelation_lm.Rmd
sync

```{r, fig.width=6, fig.height=6, message = FALSE}
## Loading the matrices CD
matrices_cd <- get.matrix.CD(path = "../Data/Simulations/Matrices", "25t_100c", verbose = TRUE, length.out = 35, cent.tend = mean)

>>>>

```{r, fig.width=6, fig.height=6, message = FALSE}
## Loading the matrices CD
matrices_cd <- get.matrix.CD(path = "../Data/Simulations/Matrices", chain = "25t_100c", verbose = TRUE, length.out = 35, cent.tend = mean)

### 2022-05-16 Analysis/Character_difference/01-Comparing_characters.Rmd
sync

```{r}
# Number of replicates:
replicates = 100
# Generate the matrices
matrices <- replicate(replicates, make.a.matrix(), simplify = FALSE)

@@

```{r, fig.width = 12, fig.height = 12}
op <- par(mfrow = c(2,2), bty = "n")
hist(characters_differences_distribution, breaks = 40, main = "Characters Difference distribution",
    xlab = "Characters Differences")
hist(characters_correlation_distribution, breaks = 40, main = "Characters Correlation distribution",
    xlab = "Characters Correlation")
plot(density(residuals), main = "Difference between both methods",
    xlab = "Residuals")
par(op)
```

@@

```{r, fig.width = 10, fig.height = 10}
plot(first_character_differences[,1], type = "l", col = "lightblue", ylim = c(0,1), xlab = "",
    ylab = "", main = "Characters comparison (matrix 80x400)")
lines(first_character_correlation[,1], col = "yellow", lty = 3)
for(replicate in 2:replicates) {
    lines(first_character_differences[,replicate], col = "lightblue")
    lines(first_character_correlation[,replicate], col = "yellow", lty = 3)
}
# Adding the medians
lines(median_first_character_differences, col = "blue")
lines(median_first_character_correlation, col = "orange")
legend("topleft", legend = c("Differences", "Correlation"), lty = 1, xjust = 1,
    yjust = 1, col = c("blue", "orange"))
```

>>>>

```{r, eval = TRUE}
# Number of replicates:
replicates = 100
# Generate the matrices
matrices <- replicate(replicates, make.a.matrix(), simplify = FALSE)

@@

```{r, fig.width = 12, fig.height = 12, eval = TRUE}
op <- par(mfrow = c(2,2), bty = "n")
hist(characters_differences_distribution, breaks = 40, main = "Characters Difference distribution",
    xlab = "Characters Differences")
hist(characters_correlation_distribution, breaks = 40, main = "Characters Correlation distribution",
    xlab = "Characters Correlation")
plot(density(residuals), main = "Difference between both methods",
    xlab = "Residuals")
par(op)
```

@@

```{r, fig.width = 10, fig.height = 10, eval = TRUE}
plot(first_character_differences[,1], type = "l", col = "lightblue", ylim = c(0,1), xlab = "",
    ylab = "", main = "Characters comparison (matrix 80x400)")
lines(first_character_correlation[,1], col = "yellow", lty = 3)
for(replicate in 2:replicates) {
    lines(first_character_differences[,replicate], col = "lightblue")
    lines(first_character_correlation[,replicate], col = "yellow", lty = 3)
}
# Adding the medians
lines(median_first_character_differences, col = "blue")
lines(median_first_character_correlation, col = "orange")
legend("topleft", legend = c("Differences", "Correlation"), lty = 1, xjust = 1,
    yjust = 1, col = c("blue", "orange"))
```

### 2022-05-16 Analysis/Character_difference/02-Modifying_matrices.Rmd
sync

## The cran version of diversitree
if(!require(diversitree)) install.packages("diversitree")
```

@@

```{r, fig.width=12, fig.height=12, eval = FALSE, echo = FALSE}
# pdf("../../Writing/Figures/Modif_matrix.pdf", width = 7.2, height = 4.5)
par(mfrow = c(2, 3), bty = "n", mar = c(1,1,1,1))
## Tree
plot(tree, cex = 0.8, main = "A - Simulated tree")
## Normal matrix
plot(char_diff_matrix_norm, type = "matrix", main = "B - Normal matrix", legend = FALSE)
## Empty plot
plot(0,0, col = "white", xaxt = 'n', yaxt = 'n', xlab = "", ylab = "")
## Maximised matrix
plot(char_diff_matrix_maxi, type = "matrix", main = "C - Maximised matrix", legend = FALSE)
## Minimised matrix
plot(char_diff_matrix_mini, type = "matrix", main = "D - Minimised matrix", legend = FALSE)
## Randomised matrix
plot(char_diff_matrix_rand, type = "matrix", main = "E - Randomised matrix", legend = FALSE)
dev.off()
```

>>>>

## The cran version of diversitree
if(!require(diversitree)) install_github("richfitz/diversitree")
```

@@

```{r, fig.width=12, fig.height=12, eval = TRUE, echo = FALSE}
pdf("../../Writing/Figures/Modif_matrix2.pdf", width = 7.2, height = 4.5)
par(mfrow = c(2, 3), bty = "n", mar = c(1,1,1,1))
## Tree
plot(tree, cex = 0.8, main = "A - Starting tree")
## Normal matrix
plot(char_diff_matrix_norm, type = "matrix", main = "B - Unperturbed matrix", legend = FALSE)
## Empty plot
plot(0,0, col = "white", xaxt = 'n', yaxt = 'n', xlab = "", ylab = "")
## Maximised matrix
plot(char_diff_matrix_maxi, type = "matrix", main = "C - Minimised correlation matrix", legend = FALSE)
## Minimised matrix
plot(char_diff_matrix_mini, type = "matrix", main = "D - Maximised correlation matrix", legend = FALSE)
## Randomised matrix
plot(char_diff_matrix_rand, type = "matrix", main = "E - Randomised matrix", legend = FALSE)
dev.off()
```

### 2022-05-16 Writing/CoverLetter.tex
added repeatability statement
sync

\documentclass[11pt]{letter}
\usepackage[a4paper,left=2.5cm, right=2.5cm, top=1cm, bottom=1cm]{geometry}
\usepackage[osf]{mathpazo}
\signature{Thomas Guillerme \\ Martin Brazeau}
\address{The University of Queensland \\School of Biological Sciences \\St Lucia QLD 4067, Australia \\guillert@tcd.ie}
\longindentation=0pt
\begin{document}

@@

Despite being at the base of almost every endeavour in modern Biology, the assumption made in tree inference that phylogenetic data is independent is probably mostly erroneous.
In fact, since the advent of Cladistics in the 1950s, evolutionary biologists have made the assumption that characters used to build a phylogeny are independent despite the fact that we are looking at their variance-covariance to build phylogenetic hypothesis.
This effect is somewhat negligible in molecular phylogenetics because the huge amount of available data is thought to temper down the correlation effect.
However, in smaller morphological datasets, this can lead to pretty big biases and can easily favour on topology from another simply with a ``judicious'' choice of characters.

Our research article, entitled ``Influence of different modes of morphological character correlation on tree inference'', is - to our knowledge - the first to thoroughly test the effect of character correlation on tree topology using a thorough simulation framework ($>$ 100 CPU years worth).
Using a novel metric to measure the amount of phylogenetic correlation in a matrix, we tested different scenario that either increase or decrease the amount of correlation of characters generated from a known ``true'' tree and compare how these levels of correlation affect our ability to recover this topology using both Maximum Parsimony and Bayesian inference.

Our results suggests that strong levels of correlation can negatively impact our ability to recover the correct tree topology and more so in Maximum Parsimony than in Baysian.
However, it is encouraging to see that low levels of correlation do not especially impact the topology, at least not to the extant where researchers should specifically collect only uncorrelated characters.
Finally, we show that, for smaller datasets, Maximum Parsimony and Bayesian inference are both pretty efficient to recover the correct topology, regardless of the amount of correlation

>>>>

\documentclass[11pt]{letter}
\usepackage[a4paper,left=2.5cm, right=2.5cm, top=1cm, bottom=1cm]{geometry}
\usepackage{hyperref}
\usepackage[osf]{mathpazo}
\signature{Thomas Guillerme \\ Abigail Pastore \\ Martin Brazeau}
\address{The University of Queensland \\School of Biological Sciences \\St Lucia QLD 4067, Australia \\guillert@tcd.ie}
\longindentation=0pt
\begin{document}

@@

The assumption made in tree inference that phylogenetic data is independent is probably mostly erroneous.
This assumption about data correlation was stated since the advent of Cladistics in the 1950s but is nowadays mainly ignored in phylogenetic endeavour when using molecular data (where it can be neglected due to the huge amount of available data).
In morphological datasets, however, where the amount of characters are much smaller, correlation can lead to significant biases especially by favouring some topologies due to a specific choice of characters (whether this is done consciously by researchers or not).
With the ``resurgence'' of the use of morphological data in phylogenetic analysis (namely with the Total Evidence tip-dating method, Ronquist \textit{et al.}, 2012, Sys. Biol), it is thus important to acknowledge limitations and caveats that come with the use of such data, namely how correlation patterns in morphological datasets can effect tree inference.

In our research article, entitled ``Influence of different modes of morphological characters correlation on tree inference'', we propose the first - to our knowledge - testing of the effect of characters correlation on tree topology based on a thorough simulation framework ($>$ 100 CPU years worth).
Using a novel distance metric to measure direct phylogenetic correlation between characters, we simulated discrete morphological datasets that we then modified to increase or decrease the overall characters correlation within the datasets.
We then measured the resulting topological differences (from both maximum parsimony and Bayesian trees) to assess the effect of characters correlation in the light of our known simulated parameters.

Our results suggest that datasets that have higher levels of correlation between characters negatively impact our ability to recover the correct tree topology.
This is to be contrasted with datasets that have low levels of correlation (i.e. that are more homoplasic) which can still recover the correct topology, depending on the amount of data and the inference method used.
These results, although non-surprising to researchers in the field, are the first - to our knowledge - to actually quantify the effect of characters correlation and provides practical data and reusable code allowing researcher to effectively measure the limitations of their empirical datasets.
Furthermore, we suggest that using our proposed new metric, one could improve bootstrap procedures in phylogenetic analysis by ``biasing'' the bootstrap to favour characters with high or low correlation, depending on the purpose of the phylogenetic search.
Finally, the code and data for this whole analysis is entirely repeatable through \url{https://github.com/TGuillerme/CharactersCorrelation/}.

### 2022-05-16 Writing/Tables/Tab_pooledsmethods_test.tex
Final results tables
Updated results
bold main results
sync

% latex table generated in R 3.4.4 by xtable 1.8-2 package
% Tue Mar 27 14:03:13 2018
\begin{table}[ht]
\centering
\begin{tabular}{llr|rl}
  \hline
metric & test & bhatt.coeff & statistic & p.value \\ 
  \hline
RF & c100:c350 & \textbf{0.99} & 190357.500 & 1 \\ 
   & c100:c1000 & \textbf{0.98} & 174085.500 & \textbf{0.001} \\ 
   & c350:c1000 & \textbf{0.984} & 180460.000 & \textbf{0.032} \\ 
  Tr & c100:c350 & \textbf{0.961} & 166609.500 & \textbf{0} \\ 
   & c100:c1000 & \textbf{0.956} & 151389.500 & \textbf{0} \\ 
   & c350:c1000 & \textbf{0.981} & 178793.500 & \textbf{0.014} \\ 
   \hline
\end{tabular}
\caption{Difference between the pooled number of characters. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric wilcoxon test (with Bonferonni-Holm correciton)} 
\label{Tab_pooledscharacters_test}
\end{table}

>>>>

% latex table generated in R 4.1.3 by xtable 1.8-4 package
% Thu Mar 24 14:24:05 2022
\begin{table}[ht]
\centering
\begin{tabular}{llr|rr}
  \hline
metric & test & bhatt.coeff & statistic & p.value \\ 
  \hline
RF & bayesian vs. parsimony & 0.939 & 192659.000 & 0.000 \\ 
  Tr & bayesian vs. parsimony & 0.986 & 157677.500 & 0.041 \\ 
   \hline
\end{tabular}
\caption{Differences between the Normalised Tree Similarities in terms of clade conservation (Robinson-Foulds distances - RF) and taxa displacement (Triplets - Tr) for the two different inference methods: bayesian or maximum parsimony. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric Wilcoxon test (with Bonferonni-Holm correction).} 
\label{Tab_pooledsmethods_test}
\end{table}

### 2022-05-16 Writing/Tables/Tab_pooledstaxa_test.tex
Final results tables
Updated results
Single comparisons done
sync

% latex table generated in R 3.4.4 by xtable 1.8-2 package
% Tue Mar 27 14:03:13 2018
\begin{table}[ht]
\centering
\begin{tabular}{llr|rl}
  \hline
metric & test & bhatt.coeff & statistic & p.value \\ 
  \hline
RF & c100:c350 & \textbf{0.99} & 190357.500 & 1 \\ 
   & c100:c1000 & \textbf{0.98} & 174085.500 & \textbf{0.001} \\ 
   & c350:c1000 & \textbf{0.984} & 180460.000 & \textbf{0.032} \\ 
  Tr & c100:c350 & \textbf{0.961} & 166609.500 & \textbf{0} \\ 
   & c100:c1000 & \textbf{0.956} & 151389.500 & \textbf{0} \\ 
   & c350:c1000 & \textbf{0.981} & 178793.500 & \textbf{0.014} \\ 
   \hline
\end{tabular}
\caption{Difference between the pooled number of characters. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric wilcoxon test (with Bonferonni-Holm correciton)} 
\label{Tab_pooledscharacters_test}
\end{table}

>>>>

% latex table generated in R 4.1.3 by xtable 1.8-4 package
% Thu Mar 24 14:24:05 2022
\begin{table}[ht]
\centering
\begin{tabular}{llr|rr}
  \hline
metric & test & bhatt.coeff & statistic & p.value \\ 
  \hline
RF & t25 vs. t75 & 0.949 & 79945.000 & 0.000 \\ 
   & t25 vs. t150 & 0.954 & 75906.000 & 0.000 \\ 
   & t75 vs. t150 & 0.984 & 60328.000 & 0.654 \\ 
  Tr & t25 vs. t75 & 0.960 & 72814.000 & 0.024 \\ 
   & t25 vs. t150 & 0.961 & 72716.000 & 0.027 \\ 
   & t75 vs. t150 & 0.980 & 64637.000 & 1.000 \\ 
   \hline
\end{tabular}
\caption{Differences between the Normalised Tree Similarities in terms of clade conservation (Robinson-Foulds distances - RF) and taxa displacement (Triplets - Tr) for the three different number of taxa: 25 (t25), 75 (t75) and 150 (t150). Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric Wilcoxon test (with Bonferonni-Holm correction).} 
\label{Tab_pooledstaxa_test}
\end{table}
